When designing a computer with a custom architecture from scratch, it is important to continually test and evaluate the correctness of the solution at all possible stages, to ensure that final product is a success.
This section documents and explains the rationale behind the different types of tests that have been performed.

\section{Testing the Processor}

Barricelli's processor has been tested at four different levels: \gls{VHDL}-based unit test simulations of the different subcomponents,  \gls{VHDL}-based integration test simulations of each processing unit, \gls{VHDL}-based system test simulations of the entire system interfacing against a mock SCU and mock memory, and finally physical integration tests of the processor programmed onto the FPGA of the Barricelli.



\subsection{\gls{VHDL}-based Subcomponent Unit Test Simulations}

Unit testing VHDL entities is extremely important in a large and complex design like the Barricelli.
For this project, almost every component, perhaps except the most trivial entities, is tested in an automated or semi-automated VHDL test bench.
A tool was developed to ease the automation of VHDL test running and validation, modeled after the leading test runners in the software industry, such as JUnit\cite{junit} and Karma\cite{karma}.
This tool enabled tests to be written using easy-to-use self-evaluating tests that compare signals at specific times against expected values.

The goal of these unit tests is to ensure that the building block components work as expected when reacting to specified input.

Screenshots of simulations of these tests can be found in Appendix \ref{appendix:test-bench-documentation}.
\todo{ Make sure screenshots of as many tests as possible are available. If not, then we probably have to do references from the following tables}
\todo{we need to stash results somewhere}.

\subsubsection{Fitness Core Components}

\input{testing/components/fitness/alu}



\subsubsection{Genetic Pipeline Components}
\todo{ Insert text and tables for components used in Genetics Pipeline}
\paragraph{Selection Core}
\input{testing/components/geneticpipeline/selection_core}

\paragraph{Crossover core}
\input{testing/components/geneticpipeline/crossover_split.tex}
\input{testing/components/geneticpipeline/crossover_doublesplit.tex}
\input{testing/components/geneticpipeline/crossover_xor.tex}
\input{testing/components/geneticpipeline/crossover_core_toplevel.tex}

\paragraph{Mutation core}
\input{testing/components/geneticpipeline/mutation_core.tex}


\subsubsection{Other Components}
\todo{ Insert text and tables for components used elsewhere}

\subsection{\gls{VHDL}-based Processing Unit Integration Test Simulations}

Each processing unit, which each consists of several interconnected subcomponents, has been simulated for integration testing.
The goal of these tests are to verify that the different subcomponents interface correctly with each other, and that the behaviour of the supercomponent is as expected.


\subsection{\gls{VHDL}-based System test Simulations}
\label{section:testing:fpga:system-tests}

The toplevel simulation test bench of the Barricelli computer, which simulates the entire FPGA as a black box interfacing against the external components, supports pre-loading entire programs into a mocked instruction memory component.
The \Gls{galapagos assembler} supports outputting assembled programs compiled to one of these mock memory components, meaning that testing new programs in a simulated environment is an easy and fun process.

\todo{the title of the test should be above the table in which its results are displayed, not just as the caption (rendered below) of the table}

A formal description of the system tests performed at this level can be found in tables
\ref{testing:fitness:pipeline_test},
\ref{testing:fitness:branch_taken},
\ref{testing:fitness:branch_not_taken},
\ref{testing:fitness:conditional_taken},
\ref{testing:fitness:conditional_not_taken},
\ref{testing:fitness:load_data},
\ref{testing:fitness:store_data},
\ref{testing:fitness:store_gene},
and
\ref{testing:fitness:load_gene}.

\input{testing/fitness/pipeline_test}
\input{testing/fitness/branch_taken}
\input{testing/fitness/branch_not_taken}
\input{testing/fitness/conditional_taken}
\input{testing/fitness/conditional_not_taken}
\input{testing/fitness/store_data}
\input{testing/fitness/load_data}
\input{testing/fitness/store_gene}
\input{testing/fitness/load_gene}
%%\input{testing/tbl/flow_template}
\input{testing/tbl/genetic_color}
\input{testing/tbl/genetic_knapsack}


\subsection{Timing simulation}
\input{testing/fitness/timing-simulation}




\section{Testing the PCB}
During and after the components were soldered on the PCB board, the board were tested to ensure that the power grid were working as it was supposed to.
For the first test, it was checked that all the various LEDs on the board was working in order to verify that the board actually was powered right, and that there was
no short circuits on the power grid itself.

Some of the earliest test were also to check that the FPGA actually was working properly, and it was done by making a simple FPGA echo program to test the various pins on the FPGA.
The pins on the FPGA were tested by connecting a led to the various FPGA-headers. If the FPGA worked correctly, the led will activate, indicating the the pins actually are operating right.
When this test was conducted on the first board that were soldered, it came out that the FPGA was not "baked on" right, and that we had to start solder a new board. 

\subsection{testing the SD card}
After the completion of the soldering process for the PCB a test were also conducted in order to ensure that the 
SD card were connected right, and outputting the right signals. 
--picture of FPGA headers
\todo{the thing where we made a simple FPGA echo program for the pins, and tested the lines from the FPGA to the headers using an led. for results: we discovered a bad bake this way}

\section{Testing IO}
\input{io/testing}

\section{Testing Additional Components}

\subsection{Galapagos Assembler}

\todo{galapagos-as has a test-suite, write about it}

\section{Additional Tests}

\subsection{The Pseudo-Random Number Generator}


The pseudo-random number generator designed for the Barricelli has been tested extensively with a pseudo-random number generator test suite called DieHarder\cn.
DieHarder is a test suite which measures the ``goodness'' of a pseudo-random number generator based a number of criteria.
\todo{ what are these criteria?}

The algorithm was implemented in python and tested against the DieHarder integration suite\cn.

The shift-based algorithm used in the pseudo-random number generator scores quite poorly in the DieHarder tests when every single bit of the output is used.
However, by only using every 7th number\cn, the algorithm ranks quite well.
A condensed DieHarder test result overview can be found in Table \vref{table:dieharder-results}.
The descriptions in the table are modified from the descriptions in the output of the DieHarder test suite.

\begin{table}[H]
    \begin{tabular}{| l | l |}
    
    \hline
    Test Name & Pass? \\
    \hline
    DieHard "Birthdays Test" & FAILED \\
    \hline
    Diehard Overlapping 5-Permutations Test & FAILED \\
    \hline
    Diehard 32x32 Binary Rank Test & FAILED \\
    \hline
    Diehard 6x8 Binary Rank Test & FAILED \\
    \hline
    Diehard Bitstream Test. & FAILED \\
    \hline
    Diehard Overlapping Pairs Sparse Occupance (OPSO) & FAILED \\
    \hline
    Diehard Overlapping Quadruples Sparce Occupancy (OQSO) Test & FAILED \\
    \hline
    Diehard DNA Test & FAILED \\
    \hline
    Diehard Count the 1s (stream) (modified) Test & FAILED \\
    \hline
    Diehard Count the 1s Test (byte) (modified) & FAILED \\
    \hline
    Diehard Parking Lot Test (modified) & FAILED \\
    \hline
    Diehard Minimum Distance (2d Circle) Test & FAILED \\
    \hline
    Diehard 3d Sphere (Minimum Distance) Test & FAILED \\
    \hline
    Diehard Squeeze Test & FAILED \\
    \hline
    Diehard Sums Test & WEAK \\
    \hline
    Diehard Runs Test & FAILED \\
    \hline
    Diehard Craps Test & FAILED \\
    \hline
    Marsaglia and Tsang GCD Test & FAILED \\
    \hline
    STS Monobit Test & WEAK \\
    \hline
    STS Runs Test & PASSED \\
    \hline
    STS Serial Test & WEAK \\
    \hline
    RGB Bit Distribution Test & FAILED/WEAK \\
    \hline
    the generalized minimum distance test & FAILED \\
    \hline
    RGB Permutations Test & PASSED \\
    \hline
    RGB Lagged Sums Test & PASSED \\
    \hline
    The Kolmogorov-Smirnov Test Test & WEAK \\
    \hline
    DAB Byte Distribution Test & PASSED \\
    \hline
    DCT (Frequency Analysis) Test & FAILED \\
    \hline
    DAB Fill Tree Test & FAILED \\
    \hline
    DAB Fill Tree 2 Test & FAILED \\
    \hline
    DAB Monobit 2 Test & FAILED \\
    \hline
  \end{tabular}
  \caption{DieHarder test results of the PRNG}
  \label{testing:prng:1-time}
\end{table}


Finally, some genetics algorithms convergence tests were run, also simulated in python, using the different pseudo-random algorithm candidates as a random number source in the experiments.
Based on the results from these experiments, it is safe to conclude that, while Barricelli's pseudo-random number generator algorithm may not be best-in-class for producing convincing randomness, it is definitely good enough for problem solving using genetic algorithms, and most certainly quicker than other more ``proper'' algorithms.

\todo{ dig up some numbers, show some graphs}



\todo{The continuous ga test}
