This report is structured as follows:

Chapter 1 introduces the assignment and its interpretation. 
It also details the goals and requirements set for the project.

Chapter 2 aims to give the reader some general insight into the science and principles behind the project.
Additionally, it defines the related terms used throughout this report.

Chapter 3 contains a bird's-eye overview of the overall system architecture and its major components.

Chapter 4 gives an in depth explanation of the processor architecture, its specialized features and most important components.

Chapter 5 details the design choices taken for the different hardware components and the layout of the PCB.

Chapter 6 describes the communication means between the processor on the FPGA and the different input and output devices through the microcontroller.

Chapter 7 covers the remaining major components of the system that does not fit within the above categories.

Chapter 8 contains the different test cases used to verify the correctness of the implementation for the different components.

Chapter 9 presents the results from simulations, performance tests and energy measurements of the processor and its components.

Chapter 10 discusses the results of the tests and measurements.

Chapter 11 presents the work process throughout the whole development, implementation and testing stages.

Chapter 12 states the conclusion for the project, as well as possible further work and improvements.

Finally, there is a glossary for uncommon terms followed by appendices.

